Analyzing Trends in U.S. Residential Real Estate Prices

### 2024-04-14 outputs/paper/paper.qmd
paper updated

---
title: "TBD"
subtitle: "TBD"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: "TBD"
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Analyzing Trends in U.S. Residential Real Estate Prices"
subtitle: "A Data-Driven Approach to Understand the Market"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/House_Price.git"
date: today
date-format: long
abstract: "TBD"
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---
